### 2015-05-13 whoop.tex
update

In this work, we decided to reuse industrial-strength tools, because (i) we did not want to ``reinvent the wheel'' and (ii) these tools are already robust and battle-proven.

>>>>

Besides the Chauffeur and \whoop components of our toolchain (denoted with grey boxes in Figure~\ref{fig:whoop}), we decided to reuse other industrial-strength tools, because (i) we did not want to ``reinvent the wheel'' and (ii) these tools are robust and battle-proven in real complex software.
